Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

\subsection*{1-1}
First of all, please describe the difference between the two manuscripts.

%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

@@

@@

{ 
(ok)Result 改寫 CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 只留下 validated by GSE2837)
(ok)Figure_4_CAMK2N1_IL19.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)
\label
}
six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
}
2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

@@

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
%As in our manuscript mentioned, In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
%Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
%Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
\end{MyColorPar}

\subsection*{1-2}
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be:
"
".

@@

\subsection*{2-1}
Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.

@@

We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%as follows:
%\begin{MyColorPar}
The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
%\end{MyColorPar}

@@

\subsection*{2-2}
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

@@

\subsection*{2-3}
% strategy should changing
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

@@

*the authors should look for more data to verify these biomarkers.
% ???

% x
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

%to generalize the utility of our workflow:
%R scripts could be re-coded and applied to start a new analysis of dataset.
% *** R 的特色 邊分析解讀，一邊 coding
%Currently, less HNSCC dataset is available worldwide (Indian?) => 
%能否套用在別的 database，可以，需要標準化(fpkm or RSEM)
%It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.

\begin{figure}
    \centering
    \includegraphics[width=14cm]{Figure_1_manuscript_workflow_modify.pdf}
    \caption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export). The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different sources of databases, e.x. The NCI's TCGA Genomic Data Commons (GDC) porting to Broad Firehose, or other databases.}
    \label{fig:workflow}
\end{figure}
%(other cancer types in the TCGA database). 
%TCGA HNSCC -> TCGA CRC, TCGA LUAD, TCGA BRCA cohorts -> GEO or other uploaded cancer cohort

@@

% we plan to extend this workflow on other TCGA cancer types
%Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
% second limitation:
%In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers. However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope. Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen. It should be carefully curated to confirm the data integrity with the correct definition. We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R. The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}. Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
\end{MyColorPar}

% #####################
\subsection*{2-4}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while

The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data. It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:

@@

In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
%\end{MyColorPar}

@@

%\end{MyColorPar}   % marked in red above

@@

\subsection*{2-5}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.

@@

\subsection*{2-6}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

@@

***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section. 
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
%\subsubsection{utility of TCGA}
%%%
Usually, researchers used TCGA to find expression biomarkers...
see https://www.biostars.org/p/153013/
Tutorial: Survival analysis of TCGA patients
#integrating gene expression (RNASeq) data Why would you want to do survival
#analysis based on gene expression data? Well, let's say you have a number of
#genes that you are interested in and they are differentially expressed between
#tumor and normal samples, it would be very powerful to show that alteration in
#gene expression correlates with worse survival or earlier tumor recurrence.
#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
#https://genome-cancer.ucsc.edu/
%%%%%%%%%

***[latex line 410]
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
%% The three challenges are not "challenges" at all. The authors exaggerated the difficulties here. 
%不要誇大說明 謙虛道歉，修改說法
=> We are apology for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

%%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
%%% 
{
[main_marginSFP_HNSCC.R] line 1361
=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS_live_days /30 # derived from last followup [30]/ last known alive [31])
event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
# SLC35E2A: 9906
# SLC35E2B: 728661
}

%%%
Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

@@

% the end of response rebuttal

>>>>

\subsection*{1-1}
\begin{MyColorPar}{blue}
First of all, please describe the difference between the two manuscripts.
\end{MyColorPar}
%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

@@

Answer

@@

{ 
(ok)Result 改寫 CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 只留下 validated by GSE2837)
(ok) Figure_4_CAMK2N1_IL19.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)
\label
}

six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
}

2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

@@

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
%As in our manuscript mentioned, In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
%Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
%Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
%\end{MyColorPar}

\subsection*{1-2}
\begin{MyColorPar}{blue}
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.
\end{MyColorPar}
%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

%\begin{MyColorPar}{blue}
Answer

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129). Also, it was shown here in the following paragraph.
\begin{MyColorPar}{red}
"
"
\end{MyColorPar}

@@

\subsection*{2-1}
\begin{MyColorPar}{blue}
Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
\end{MyColorPar}

%
Answer

@@

We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

\begin{MyColorPar}{red}
The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
\end{MyColorPar}

@@

%

\subsection*{2-2}
\begin{MyColorPar}{blue}
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone
\end{MyColorPar}

%
Answer

@@

%

\subsection*{2-3}
\begin{MyColorPar}{blue}
% strategy should changing
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.
\end{MyColorPar}

%
Answer

@@

*the authors should look for more data to verify these biomarkers.
???

% xxxxx
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

%to generalize the utility of our workflow:
%R scripts could be re-coded and applied to start a new analysis of dataset.
% *** R 的特色 邊分析解讀，一邊 coding
%Currently, less HNSCC dataset is available worldwide (Indian?) => 
%能否套用在別的 database，可以，需要標準化(fpkm or RSEM)
%It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)

%Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
%Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.

%(other cancer types in the TCGA database). 
%TCGA HNSCC -> TCGA CRC, TCGA LUAD, TCGA BRCA cohorts -> GEO or other uploaded cancer cohort

@@

% we plan to extend this workflow on other TCGA cancer types
%Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
% second limitation:
%In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers. However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope. Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen. It should be carefully curated to confirm the data integrity with the correct definition. We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R. The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}. Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
%\end{MyColorPar}

% #####################
\subsection*{2-4}
\begin{MyColorPar}{blue}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
\end{MyColorPar}

%
Answer

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data. It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:

@@

In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
\end{MyColorPar}

@@

@@

\subsection*{2-5}
\begin{MyColorPar}{blue}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
\end{MyColorPar}
%
Answer

@@

%

\subsection*{2-6}
\begin{MyColorPar}{blue}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.
\end{MyColorPar}

%
Answer

@@

%%
\begin{MyColorPar}{blue} % minor comment
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
\end{MyColorPar}

The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.

\begin{MyColorPar}{red}
%\subsubsection{utility of TCGA}
%%%
Usually, researchers used TCGA to find expression biomarkers...
see https://www.biostars.org/p/153013/
Tutorial: Survival analysis of TCGA patients
#integrating gene expression (RNASeq) data Why would you want to do survival
#analysis based on gene expression data? Well, let's say you have a number of
#genes that you are interested in and they are differentially expressed between
#tumor and normal samples, it would be very powerful to show that alteration in
#gene expression correlates with worse survival or earlier tumor recurrence.
#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
#https://genome-cancer.ucsc.edu/
%%%%%%%%%
\end{MyColorPar}

%%%***[latex line 410]
\begin{MyColorPar}{blue} % minor comment
In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
\end{MyColorPar}

% 不要誇大說明 謙虛道歉
=> We are apology for exaggerating the difficulties of our workflow.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.

\begin{MyColorPar}{red}
%%%
There are three steps of biomarker discovery from survival analysis.
First, although \acrshort{tcga} genomics data was harmonized, there are 
several points should be manually investigated and cleaned.

\begin{outline}
\1 including null expressed genes, over 50\% of the cohort, 
\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
{
[main_marginSFP_HNSCC.R] line 1361
=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
OS_live_days /30 # derived from last followup [30]/ last known alive [31])
event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
R help from Jorge I Velez
[line 1654]
=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
# SLC35E2A: 9906
# SLC35E2B: 728661
}
\end{outline}

Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

@@

% the end of response rebuttal %%%%%%%%%%%%
